---
title: "Diamond"
author: "Sanmoy Paul, Sameer Acharaya, Kashyap Bhuva, Jay Bhatt"
date: "19 January 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Set Working Directory**
```{r setwd, echo=TRUE} 
setwd("C:\\F\\NMIMS\\DataScience\\Sem-2\\ML-R")
```

**Load Libraries**
```{r LoadLibraries, echo=TRUE}  
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(gridExtra)
library(plotly)
library(Hmisc)
library(corrgram)
library(caTools)
``` 

**Read Csv**
```{r readCSV, echo=TRUE}
dataset <- read.csv("./data/diamonds.csv", header = T, stringsAsFactors = F)
```   

**Read First 6 recs**
```{r ReadFirst, echo=TRUE}
head(dataset)
```
**Read Last 6 recs**
```{r ReadLast, echo=TRUE}
tail(dataset)
```

**Structure of the data frame**
```{r struc, echo=TRUE}
str(dataset)
glimpse(dataset)
```

**No of Cols**
```{r nCol, echo=TRUE}
ncol(dataset)
```

**No of rows**
```{r nRow, echo=TRUE}
nrow(dataset)
```

**Names**
```{r colNames, echo=TRUE}
names(dataset)
colnames(dataset)
```  

**Detect NAs**
```{r detectNA, echo=TRUE}
detectNAs<-function(x){
  return(sum(is.na(x)))
}
lapply(dataset, detectNAs)
``` 

**DetectSpace**
```{r detectSpace, echo=TRUE}
detectSpace <- function(x){
  if(class(x)=="character")
    return(sum(str_trim(x)==""))
  else
    return("Not a Character")
}
sapply(dataset, detectSpace)
```  

**Clean Data**
```{r cleanData, echo=TRUE}
dataset$cut[str_trim(dataset$cut)==""] <- NA
dataset$color[str_trim(dataset$color)==""] <- NA
dataset$clarity[str_trim(dataset$clarity)==""] <- NA

which(is.na(dataset$cut))
which(is.na(dataset$color))
which(is.na(dataset$clarity))
``` 
**Remove NA's**
```{r removeNas, echo=TRUE}
datasetGood <- na.omit(dataset)
nrow(datasetGood)
```  

**Summary stat**
```{r summaryStat, echo=TRUE}
summary(dataset)
```  

**Freq dist of Price**
```{r freqDist, echo=TRUE}
p1<- ggplot(datasetGood, aes(x=price))+
  geom_histogram(binwidth = 1)+
  labs(title="Price Distribution")+
  labs(x="Price")

p2<-ggplot(datasetGood, aes(x=carat))+
  geom_histogram(binwidth=0.1)+
  labs(title="Carat Distribution")+
  labs(x="Carat")

p3<-ggplot(datasetGood, aes(x=depth))+
  geom_histogram(binwidth=0.5)+
  labs(title="Depth Distribution")+
  labs(x="Depth")

p4<-ggplot(datasetGood, aes(x=table))+
  geom_histogram(binwidth=0.5)+
  labs(title="Table Distribution")+
  labs(x="Table")

grid.arrange(p1, p2, p3, p4, nrow=2, ncol=2)
``` 

**Comparision of cut with price**
```{r comparisionGraph, echo=TRUE}
g1<-ggplot(datasetGood, aes(x=color, y=price))+
  geom_point(position="jitter")+
  labs(title="Color v/s Price")+
  labs(x="Color")+
  labs(y="Price")

g2<-ggplot(datasetGood, aes(x=color, y=price, fill=color))+
  geom_bar(stat="identity", position="dodge")+
  labs(title="Color v/s Price")+
  labs(x="Color")+
  labs(y="Price")


g3<-ggplot(datasetGood, aes(x=cut, fill=color))+
  geom_bar(stat="count", position="dodge")+
  labs(title="Count of Color by Cut")+
  labs(x="Cut")+
  labs(y="Color")

g4<-ggplot(datasetGood, aes(x=cut, fill=clarity))+
  geom_bar(stat="count", position="dodge")+
  labs(title="Count of Clarity by Cut")+
  labs(x="Cut")+
  labs(y="Clarity")

grid.arrange(g1, g2, g3, g4, nrow=2, ncol=2)
```  

**Chisq Test**
***H0: Clarity is independent on cut***
***H1: Clarity is dependent on cut***
```{r chisqTest, echo=TRUE}
cTable <- table(datasetGood$cut, datasetGood$clarity)
cTable
chisq.test(cTable)
```  
***Reject Null Hypothesis at significance level=0.05***


**Annova**
***H0: Price is independent on cut and clarity***
***H1: Price is dependent on cut and clarity***
```{r annovaCut&Clarity, echo=TRUE}
datasetAnn <- datasetGood[, 1:7]
datasetAnn$cut <- factor(datasetAnn$cut, levels=c("Fair", "Good", "Ideal", "Premium", "Very Good"), labels = c(1,2,3,4,5))
datasetAnn$clarity <- factor(datasetAnn$clarity, levels=c("I1", "IF", "SI1", "SI2", "VS1", "VS2", "VVS1", "VVS2"), labels = c(1,2,3,4,5,6,7,8))
datasetAnn$color <- factor(datasetAnn$color, levels=c("D", "E", "F", "G", "H", "I", "J"), labels = c(1,2,3,4,5,6,7))
annova=aov(price ~ (cut + clarity + cut*clarity), data=datasetAnn)
summary(annova)
```  
***Accept Alt Hypothesis, both cut and clarity is dependent on price***


***H0: Price is independent on color and cut***
***H1: Price is dependent on color and cut***
```{r annovaCut&Color, echo=TRUE}
annova=aov(price ~ (cut + color + cut*color), data=datasetAnn)
summary(annova)
```  
***Accept Alt Hypothesis, both cut and color is dependent on price***

**H0: Price is independent on color and clarity**
**H1: Price is dependent on color and clarity**
```{r annovaColor&Clarity, echo=TRUE}
annova=aov(price ~ (color + clarity + color*clarity), data=datasetAnn)
summary(annova)
```   
***Accept Alt Hypothesis, both clarity and color is dependent on price***


**Box plot**
```{r boxPlot, echo=TRUE}
b1 <- ggplot(datasetAnn, aes(x=cut, y=price)) +
  geom_boxplot(aes(fill=cut)) +
  labs(title="cut & price") +
  labs(x="Cut") +
  labs(y="Price")

b2 <- ggplot(datasetAnn, aes(x=color, y=price)) +
  geom_boxplot(aes(fill=color)) +
  labs(title="color & price") +
  labs(x="Color") +
  labs(y="Price")


b3 <- ggplot(datasetAnn, aes(x=clarity, y=price)) +
  geom_boxplot(aes(fill=clarity)) +
  labs(title="clarity & price") +
  labs(x="Clarity") +
  labs(y="Price")

grid.arrange(b1, b2, b3, nrow=3, ncol=1)
```  


**Correlation**
```{r correlation, echo=TRUE}
rcorr(as.matrix(datasetAnn))
```  
**Correlation Plot**
```{r correlationPlot, echo=TRUE}
col.corrgram <- function(ncol){   
  colorRampPalette(c("darkgoldenrod4", "burlywood1",
                     "darkkhaki", "darkgreen"))(ncol)} 
corrgram(datasetAnn, order=TRUE, lower.panel=panel.shade, 
         upper.panel=panel.pie, text.panel=panel.txt, 
         main="Correlogram of Car Mileage Data (PC2/PC1 Order)")
```    

**Multiple Regression**
***DependentVariable=Price***
```{r multipleReg, echo=TRUE}
datasetAnn <- datasetAnn[c(2,3,4,1,5,6,7)]
set.seed(123)
```  
***Split the data into training and test set***
```{r splittingDataset, echo=TRUE}
split<-sample.split(datasetAnn$price, SplitRatio = 0.8)
training_set<-subset(datasetAnn, split==TRUE)
test_set<-subset(datasetAnn, split==FALSE)
```  

***Scaling***
```{r featureScaling, echo=TRUE}
training_set[,4:7]<-scale(training_set[,4:7])
test_set[,4:7]<-scale(test_set[, 4:7])
```  
***Build Multiple Regression Model***
```{r modelBuild, echo=TRUE}
regressor1<- lm(formula=price~., data=training_set)
summary(regressor1)
```  
***predict on test data***
```{r predict, echo=TRUE}
y_pred<-predict(regressor1, newdata = test_set)
head(y_pred)
```  
**Linear Regression**
***Dependent=Price***
***Independent=carat***
```{r linearReg, echo=TRUE}
datasetReg<-subset(datasetAnn, select = c(4,7))
set.seed(123)
```  
***Split the data into training and test set***
```{r splittingDataset2, echo=TRUE}
split<-sample.split(datasetReg$price, SplitRatio = 0.8)
training_set2<-subset(datasetReg, split==TRUE)
test_set2<-subset(datasetReg, split==FALSE)
```  

***Scaling***
```{r featureScaling2, echo=TRUE}
training_set2[,1:2]<-scale(training_set2[,1:2])
test_set2[,1:2]<-scale(test_set2[, 1:2])
```  
***Build Linear Model***
```{r buildLinearModel, echo=TRUE}
regressor2<- lm(formula=price~carat, data=training_set2)
summary(regressor2)
```  
***predict on test data***
```{r prediction, echo=TRUE}
y_pred<-predict(regressor2, newdata = test_set2)
head(y_pred)
```  
**Plot regression**
```{r plotReg, echo=TRUE}
r1<-ggplot(training_set2, aes(x=carat, y=price))+
  geom_point()+geom_smooth(method="lm", se=FALSE)+
  labs(title="TrainingData-Carat v/s Price")+
  labs("Carat")+
  labs("Price")


r2<-ggplot()+
  geom_point(aes(x=test_set2$carat, y=test_set2$price), color="red")+geom_line(aes(x=training_set2$carat, y=predict(regressor2, newdata = training_set2)))+
  labs(title="TestData-Carat v/s Price")+
  labs("Carat")+
  labs("Price")

grid.arrange(r1, r2, nrow=2, ncol=1)
```